---
title: "rperseus Vignette"
author: "David Ranzolin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

### Introduction

The workhorse of `rperseus` is `get_perseus_text`. You pass one argument to this function: `text_urn`. URNs (Uniform Resource Number) can be located within the `perseus_catalog` object, which is lazily loaded on `library(rperseus)`. I recommend scanning the catalog before selecting a text.

```{r}
library(rperseus)
head(perseus_catalog)
```

A snapshot of available authors:

```{r warning=FALSE, message=FALSE}
library(dplyr)
count(perseus_catalog, groupname, sort = TRUE)
```

### Getting a Text

Once you've identified the relevant URN, paste it into a call to `get_perseus_text`. Here I've called for the Greek text of Plato's *Crito*:

```{r}
crito <- get_perseus_text(text_urn = "urn:cts:greekLit:tlg0059.tlg003.perseus-grc2")
crito$text[1]
```

### Getting Multiple Texts with the tidyverse

You can collect all of Plato's available English translations with the `tidyverse:`

```{r eval = FALSE}
plato <- perseus_catalog %>% 
  filter(groupname == "Plato",
         language == "eng") %>% 
  pull(urn) %>% 
  map_df(get_perseus_text)
```




